---
title: "Reproducible Pitch Presentation"
author: "Kenneth Leong"
date: "Sunday, 22 Feb, 2015"
output:
  ioslides_presentation:
    transition: faster
runtime: shiny
---

```{r echo=FALSE, message=FALSE}
#Loading required packages
if(!require(dplyr)) {install.packages("dplyr")}
if(!require(ggvis)) {install.packages("ggvis")}
if(!require(shiny)) {install.packages("shiny")}
```

## Here's what I need

- 5 slides to pitch our idea done in Slidify or Rstudio Presenter
- This presentation pushed to github or Rpubs
- A link to github or Rpubs presentation pasted into the text box in submission page

## The Presentation must satisfy the following

1. It must be done in Slidify or Rstudio Presenter
2. It must be 5 pages
3. It must be hosted on github or Rpubs
4. It must contained some embedded R code that gets run when slidifying the document

## Some Embedded R Code

```{r, echo = FALSE, message = FALSE, fig.width = 6, fig.height = 4}
mtcars %>%
  ggvis(x=~mpg)
```

## An Interactive Table

```{r, echo=FALSE, fig.height=4, fig.width=8}
mtcars %>%
  group_by(rownames(mtcars)) %>%
  summarise(mpg=mean(mpg), wt=mean(wt)) %>%
  renderDataTable()
```